\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{Abstract}

Digital transformation is often discussed in the context of large enterprises; however, small and medium-sized enterprises (SMEs) face the greatest challenges in inventory management. Maintaining manual or spreadsheet-based management methods often leads to data errors and imbalances between excess inventory and out-of-stock situations.

This thesis details the design and development process of "Warehouse Pro," a comprehensive warehouse management solution aimed at optimizing operational performance through modern web technologies and Artificial Intelligence (AI). The application is built on ASP.NET Core 8.0 for a robust and secure backend and ReactJS for an optimized user interface.

The system's breakthrough feature is the integration of an AI Chatbot Assistant based on the Semantic Kernel architecture and the large language model (Llama 3.1). This assistant not only supports data querying using natural language but also has the ability to perform direct administrative tasks, helping managers interact with the system intelligently and quickly. In addition, the system is equipped with automatic communication features, allowing for email notifications based on pre-designed templates as soon as inventory transactions occur. The integration of SignalR provides real-time notifications and data updates, ensuring seamless coordination between warehouse staff and management.

The project's outcome is a complete system supporting the management of the entire product lifecycle, from import and export to accounts receivable management and detailed reporting. Real-world testing has shown that the solution significantly reduces manual data entry time, increases transparency in email communication with partners, and modernizes operational processes, demonstrating the practical applicability of generative AI technology in solving management problems for small and medium-sized enterprises.